The Driving Forces Behind API Evolution

### 2015-05-19 thesis/paper.tex
implic academ

@@

\subsection{Implications for Academia} 
Reverse engineering/types: 
       Since we were able to correctly analyse which types they were, it should encourage academia to do more studies which reverse engineer theories etc.

Laws:
       Some laws don't apply. Consider inverting the law of org stab for APIs
       Since motives are reverse engineerable, it should encourage more ppl to do similar studies

%       -How will our study help other researchers?
%       -How are the results valuable?

>>>>

\newpage

@@

\newpage

\subsection{Implications for Academia} 
The implications of our findings should encourage academia to further study APIs by relating them to existing software evolution theories. Considering that we were able to successfully reverse engineer the changes made to the API in this study, it opens up possibilities to base future research on, for example, the types of software evolution and software maintenance. Since the kappa analysis showed that there was a high level of agreement between our predictions and the actual motives to the change, it shows that the types of software evolution and software maintenance could even be used as a base for a large-scale quantitative analysis to map the types of changes made to APIs.

By analysing the API based on Lehman's laws, we were able to find that the law of Conservation of Organisational Stability did not apply to the API examined in this study. Our results suggest that the opposite of what the law says in its current form is closer to the truth (!!!reword) for APIs. Since we only studied one API, we cannot safely refute the law or propose a new formulation of it. We do, however, believe that academia should be wary of assuming that this law is true for APIs.

\newpage
